### 2014-02-27 paper/concrete.tex
Finish iso proofs.
Signed-off-by: Edward Z. Yang <ezyang@cs.stanford.edu>

\begin{definition}[Information-flow control language]
    An information-flow control language L is a tuple $(|C|, |C|^*, |.->|,
    |erasef l|)$, where $c \in |C|$ is the type of machine configurations,
    $|C|^*$ is the type of erased machine configurations, |.->| is a
    reduction relation between machine configurations and $|erasef l|$
    is an erasure function from machine configurations to erased machine
    configurations.
\end{definition}

@@

\begin{definition}[Isomorphism of information-flow control languages]
    Two languages
    \tar{L} $(|tC|, |tC|^*, \tar{|.->|}, \tar{|erasef l|})$ and \ifc{L} $(|iC|, |iC|^*, \ifc{|.->|}, \ifc{|erasef l|})$ are isomorphic if there exist (total) functions
    $f : |tC -> iC|$ and $f^{-1} : |iC -> tC|$ such that $f \circ f^{-1}
    = id_{|tC|}$, $f^{-1} \circ f = id_{|iC|}$, and that $f$ and $f^{-1}$ are
    functorial over $l$-equivalences (i.e. if $|tc|\ \tar{\approx_l}\
    |tc'|$ then $f(|tc|)\ \ifc{\approx_l}\ f(|tc'|)$ and vice-versa).
\end{definition}

@@

\begin{proof}
    Easily shown by transporting configurations and reduction derivations
    from \tar{L} to \ifc{L}, applying TSNI, and then transporting the resulting
    configuration and multi-step derivation back.
\end{proof}

>>>>

\Red{Move these definitions earlier}

\begin{definition}[Information-flow control language]
    An information-flow control language L is a tuple $(|C|, |C|^*, |.->|,
    |erasef l|)$, where $c \in |C|$ is the type of machine configurations,
    $|C|^*$ is the type of erased machine configurations, |.->| is a
    reduction relation between machine configurations and $|erasef l|$
    is an erasure function from machine configurations to erased machine
    configurations.  For sequential languages, we may also speak of
    values, e.g. a configurations $V \subseteq |C|$ for which there are
    no possible further transitions.
\end{definition}

@@

Before we show isomorphism preserves termination sensitive
non-interference, we'd like to remark that one can safely remove transitions
and preserve termination \emph{insensitive} interference:

\begin{definition}[Inclusion of information-flow control languages]
    A language $(|tC|, |tC|^*, \tar{|V|}, \tar{|.->|}, \tar{|erasef l|})$ is
    included in $(|iC|, |iC|^*, \ifc{|V|}, \ifc{|.->|}, \ifc{|erasef
    l|})$ if there exists a total function $f : |tC -> iC|$ such that
    $f$ is a bijection over $l$-equivalences ($|tc|\ \tar{\approx_l}\
    |tc'|$ if and only if $f(|tc|)\ \ifc{\approx_l}\ f(|tc'|)$),
    preserves values (if $|tc| \subseteq \tar{|V|}$ then $|ic| \subseteq
    \ifc{|V|}$) and is functorial over $|.->|$ (if $|tc|\ \tar{|.->|}\
    |tc'|$ then $f(|tc|)\ \ifc{|.->|}\ f(|tc'|)$).
\end{definition}

\begin{theorem}[Isomorphism preserves termination insensitive non-interference]
    If \tar{L} is included in \ifc{L}, and \ifc{L} satisfies TINI, then
    \tar{L} satisfies TINI.
\end{theorem}

\begin{proof}
    Shown by transporting configurations and reduction derivations
    from \tar{L} to \ifc{L}, applying TINI and transporting the resulting
    equivalence back using bijectivity of $f$ over $l$-equivalences.
\end{proof}

Now we strengthen the condition to show TSNI:

\begin{definition}[Isomorphism of information-flow control languages]
    A language $(|tC|, |tC|^*, \tar{|.->|}, \tar{|erasef l|})$ is
    isomorphic to \ifc{L} $(|iC|, |iC|^*, \ifc{|.->|}, \ifc{|erasef l|})$ are isomorphic if there exist total functions
    $f : |tC -> iC|$ and $f^{-1} : |iC -> tC|$ such that $f \circ f^{-1}
    = id_{|tC|}$, $f^{-1} \circ f = id_{|iC|}$, and $f$ and $f^{-1}$ are
    functorial over both $l$-equivalences (if $|tc|\ \tar{\approx_l}\
    |tc'|$ then $f(|tc|)\ \ifc{\approx_l}\ f(|tc'|)$ and vice-versa) and
    $|.->|$ (if $|tc|\ \tar{|.->|}\ |tc'|$ then $f(|tc|)\ \ifc{|.->|}\ f(|tc'|)$ and vice versa).
\end{definition}

@@

\begin{proof}
    Shown by transporting configurations and reduction derivations from
    \tar{L} to \ifc{L}, applying TSNI, and then transporting the
    resulting configuration and multi-step derivation back.
\end{proof}
